---
title: "FDA Project - Walmart Store Sales Forecasting"
author: "17MIS1137 | 17MIS1194"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---
# __INTRODUCTION__

## Objectives
* To perform exploratory analysis on the dataset
* To build a time series model
* To Predict the department-wide-sales for each store

## Dataset description
The Kaggle dataset contains historical sales data for 45 Walmart stores located in different regions. Each store contains a number of departments, and we have to
predict the department-wide sales for each store.The datasets included information about : 

* **train** dataset

    + *Store* - the store number
    + *Dept* - the department number
    + *Date* - the week 
    + *Weekly_Sales* - sales for the given department in the given store and department
    + *IsHoliday* - whether the week was a special holiday week

Additional data related to the store, department, and regional promotional activity for the given dates were available in the dataset *features*. The variables included in this dataset are shown below.

* **features** dataset

    + *Store* - the store number
    + *Date* - the week 
    + *Temperature*- average temperature in the region
    + *Fuel Price* - cost of fuel in the region
    + *MarkDown 1-5* - anonymised data related to promotional markdowns that Walmart was running
    + *CPI* - consumer price index
    + *Unemployment* - the unemployment rate
    + *IsHoliday* - whether the week was a special holiday week
     
Anonymised information about the 45 stores, indicating the type and size of store, were also available in the dataset *stores*.  
    
* **stores** dataset

    + *Store* - the store number
    + *Type* - type of the store (A, B, C)
    + *Size* - size of the store


### Installing the packages and dependencies

```{r message = FALSE, warning = FALSE}
library(timeDate)
library(randomForest)
library(ggplot2)
library(reshape2)
library(dplyr)
library(magrittr)
library(fpp)
library(rlist)
library(tidyverse)
```

### Importing Dataset

```{r}
stores <- read.csv("./Dataset/stores.csv")
features <- read.csv("./Dataset/features.csv")
train <- read.csv("./Dataset/train.csv")
```

# _EXPLORING THE DATASET__
```{r}
str(stores)
str(train)
```

### __Distribution of variables__
```{r}
par(mfrow=c(3,2))
hist(train$Store, col = 'light pink', main = "Stores")
hist(features$Temperature, col = 'light pink', main = "Temperature")
hist(features$Fuel_Price, col = 'light pink', main = "Fuel Price")
hist(features$CPI, col = 'light pink', main = "CPI")
hist(features$Unemployment, col = 'light pink', main = "Unemployment")
hist(stores$Size, col = 'light pink', main = "Store Size")

```

Temperature, Fuel Price and Unemployment are fairly normally distributed. Store Sizes have brackets on both ends indicating large number of large and small stores. The medium sized stores are very few in comparison in this dataset. We might need to do some transformation of this data


```{r}
#Merge store data with train data
tdata <- merge(x=train,y=stores,all.x = TRUE)
#merge features with train data
train<-merge(x=tdata, y= features, all.x = TRUE)
train_format <- data.frame(Store=factor(),Date=as.Date(character()),CPI = double(), Unemployment = double(), Weekly_Sales=double(),IsHoliday=logical(),Type=factor())
```

```{r}
#sum of weekly sales of all dept
sum_weekly_sales <- function(){
  for(n in 1:45){
    per_store <- train %>% filter(Store == n)
    each_date <- unique(train$Date)
    
    for(dates in seq_along(each_date)){
      curdate <- unique(train$Date)[[dates]]
      dataDates <- per_store %>% filter(Date==curdate)
      
      net_sales <- unlist(sum(dataDates$Weekly_Sales))
      nrow <- data.frame(Store=n,Date=curdate,Weekly_Sales=net_sales,CPI = dataDates$CPI[[1]], Unemployment = dataDates$Unemployment[[1]], IsHoliday=dataDates$IsHoliday[[1]],Type=dataDates$Type[[1]])
      train_format <- rbind(train_format,nrow)
      
      
    }
  }
  return(train_format)
  
}

```


### Sum of the weekly sales of all department-wide stores
```{r}
train_final <- sum_weekly_sales()
head(train_final)
```

```{r}
par(mfrow = c(1,2))
hist(train_final$Weekly_Sales, col = 'light green', main = "Weekly Sales Original", xlab = "Weekly Sales")
hist(log(train_final$Weekly_Sales), col = 'light green', main = "Weekly Sales Transformed", xlab ='log(Weekly Sales)')
```
# __ARIMA MODEL__

ARIMA models aim to describe the autocorrelations in the data and are generally used to make forecasts rather than predicting sales in the past. The nature of the algorithm requires that the data are transformed into a time series format and that there are no missing observations (weeks). Thus, creating a train/test set for time-series problems becomes tricky because the time component has to be taken into account..

```{r}
#AUTO ARIMA
train.Store1 <- train_final %>% filter(Store == 1)
trainStore1.ts <- ts(train.Store1, frequency = 52, start = c(2010,5), end = c(2012,42))
train.train1 <- window(trainStore1.ts, start = c(2010,5), end = c(2011,52))
train.test1 <- window(trainStore1.ts, start = c(2012,1), end = c(2012,42))
trainArima1 <- auto.arima(train.train1[,3], approximation = TRUE)
trainArima1
trainArimaForecast1 <- forecast(trainArima1, h = 42)
plot(trainArimaForecast1, ylab = "Weekly Sales")
train.test1[,3]
accuracy(trainArimaForecast1,train.test1[,3]) 
```

```{r}
#fit <- lm(Weekly_Sales ~.-Date-Type-CPI, data=train_final)
#INITIAL ANALYSIS
plot(decompose(trainStore1.ts[,3]))
adf.test(trainStore1.ts[,3], k = 20)
```
### TRAINING ON STORE NUMBER 45 
```{r}
train.Store45 <- train_final %>% filter(Store == 45)
trainStore45.ts <- ts(train.Store45, frequency = 52, start = c(2010,5), end = c(2012,42))
train.train45 <- window(trainStore45.ts, start = c(2010,5), end = c(2011,52))
train.test45 <- window(trainStore45.ts, start = c(2012,1), end = c(2012,42))
trainArima45 <- auto.arima(train.train45[,3], approximation = TRUE)
summary(trainArima45)
trainArimaForecast45 <- forecast(trainArima45, h = 42)
plot(trainArimaForecast45, ylab = "Weekly Sales")
accuracy(trainArimaForecast45,train.test45[,3]) 
```
# __NNETAR MODEL__
some neural network model idk

```{r}
#NNETAR
train.Store1 <- train_final %>% filter(Store == 1)
trainStore1.ts <- ts(train.Store1, frequency = 52, start = c(2010,5), end = c(2012,42))
train.train1 <- window(trainStore1.ts, start = c(2010,5), end = c(2011,52))
train.test1 <- window(trainStore1.ts, start = c(2012,1), end = c(2012,42))
train1Net <- nnetar(train.train1[,3])
train1Net
train1Netfo <- forecast(train1Net, h = 42)
plot(train1Netfo, ylab ="Weekly Sales")
accuracy(train1Netfo,train.test1[,3])
```

```{r}
#testing NNAR on store 45
train.Store45 <- train_final %>% filter(Store == 45)
trainStore45.ts <- ts(train.Store45, frequency = 52, start = c(2010,5), end = c(2012,42))
train.train45 <- window(trainStore45.ts, start = c(2010,5), end = c(2011,52))
train.test45 <- window(trainStore45.ts, start = c(2012,1), end = c(2012,42))
train45Net <- nnetar(train.train45[,3])
train45Net
train45Netfo <- forecast(train45Net, h = 42)
plot(train45Netfo)
accuracy(train45Netfo,train.test1[,3])

```
# __TIME SERIES REGRESSION__
```{r}
#Time Series Regression
train.Store1 <- train_final %>% filter(Store == 1)
trainStore1.ts <- ts(train.Store1, frequency = 52, start = c(2010,5), end = c(2012,42))
plot(decompose(trainStore1.ts[,3]))
train.train1 <- window(trainStore1.ts, start = c(2010,5), end = c(2011,52))
train.test1 <- window(trainStore1.ts, start = c(2012,1), end = c(2012,42))
store1.fit <- tslm(train.train1[,3] ~ trend + season)
summary(store1.fit)
accuracy(store1.fit)
trainTSLMfor1 <- forecast(store1.fit, h = 42)
plot(trainTSLMfor1, ylab = "Weekly Sales")
accuracy(trainTSLMfor1, train.test1[,3])
```

```{r}
#Decompose for store 45
train.Store45 <- train_final %>% filter(Store == 45)
trainStore45.ts <- ts(train.Store45, frequency = 52, start = c(2010,5), end = c(2012,42))
plot(decompose(trainStore45.ts[,3]))
```
```{r}
#COmpare store 1 and store 45
train.train45 <- window(trainStore45.ts, start = c(2010,5), end = c(2011,52))
train.test45 <- window(trainStore45.ts, start = c(2012,1), end = c(2012,42))
store45.fit <- tslm(train.train45[,3] ~ trend + season)
summary(store45.fit)
accuracy(store45.fit)
trainTSLMfor45 <- forecast(store45.fit, h = 42)
accuracy(trainTSLMfor45, train.test45[,3])
plot(trainTSLMfor45, ylab = "Weekly Sales")
ts.plot(trainStore1.ts,trainStore45.ts, gpars=list(xlab="year", ylab="Weekly Sales", col=c(3:4), lty = c(1,2)))
legend("topright", c("Store 1 Data", "Store 45 Data"), cex = 0.85, lty = c(1,2), col = c("green", "blue"))
```
# FINAL TIME SERIES MODEL FOR PREDICTION 

```{r}
#FINAL MODEL PREDICTION
dates <- seq(as.Date("2012-11-02"),as.Date("2013-11-01"),7)

train.Store1 <- train_final %>% filter(Store == 1)
trainStore1.ts <- ts(train.Store1, frequency = 52, start = c(2010,5), end = c(2012,42))
store1.fit <- tslm(trainStore1.ts[,3] ~ trend + season)
trainTSLMfor1 <- forecast(store1.fit, h = 53)
df1 <- rep(1, len = 53)
predict1 <- as.numeric(trainTSLMfor1$mean)
nrow1 <- data.frame(Store=df1,Date=dates,Weekly_Sales=predict1)
```


```{r}
train.Store2 <- train_final %>% filter(Store == 2)
trainStore2.ts <- ts(train.Store2, frequency = 52, start = c(2010,5), end = c(2012,42))
store2.fit <- tslm(trainStore2.ts[,3] ~ trend + season)
trainTSLMfor2 <- forecast(store2.fit, h = 53)
trainTSLMfor2
df2 <- rep(2, len = 53)
predict2 <- as.numeric(trainTSLMfor2$mean)
nrow2 <- data.frame(Store=df2,Date=dates,Weekly_Sales=predict2)
```


```{r}
train.Store3 <- train_final %>% filter(Store == 3)
trainStore3.ts <- ts(train.Store3, frequency = 52, start = c(2010,5), end = c(2012,42))
store3.fit <- tslm(trainStore3.ts[,3] ~ trend + season)
trainTSLMfor3 <- forecast(store3.fit, h = 53)
trainTSLMfor3
df3 <- rep(3, len = 53)
predict3 <- as.numeric(trainTSLMfor3$mean)
nrow3 <- data.frame(Store=df3,Date=dates,Weekly_Sales=predict3)
```


```{r}
train.Store4 <- train_final %>% filter(Store == 4)
trainStore4.ts <- ts(train.Store4, frequency = 52, start = c(2010,5), end = c(2012,42))
store4.fit <- tslm(trainStore4.ts[,3] ~ trend + season)
trainTSLMfor4 <- forecast(store4.fit, h = 53)
trainTSLMfor4
df4 <- rep(4, len = 53)
predict4 <- as.numeric(trainTSLMfor4$mean)
nrow4 <- data.frame(Store=df4,Date=dates,Weekly_Sales=predict4)
```


```{r}
train.Store5 <- train_final %>% filter(Store == 5)
trainStore5.ts <- ts(train.Store5, frequency = 52, start = c(2010,5), end = c(2012,42))
store5.fit <- tslm(trainStore5.ts[,3] ~ trend + season)
trainTSLMfor5 <- forecast(store5.fit, h = 53)
trainTSLMfor5
df5 <- rep(5, len = 53)
predict5 <- as.numeric(trainTSLMfor5$mean)
nrow5 <- data.frame(Store=df5,Date=dates,Weekly_Sales=predict5)
```


```{r}
train.Store6 <- train_final %>% filter(Store == 6)
trainStore6.ts <- ts(train.Store6, frequency = 52, start = c(2010,5), end = c(2012,42))
store6.fit <- tslm(trainStore6.ts[,3] ~ trend + season)
trainTSLMfor6 <- forecast(store6.fit, h = 53)
trainTSLMfor6
df6 <- rep(6, len = 53)
predict6 <- as.numeric(trainTSLMfor6$mean)
nrow6 <- data.frame(Store=df6,Date=dates,Weekly_Sales=predict6)
```


```{r}
train.Store7 <- train_final %>% filter(Store == 7)
trainStore7.ts <- ts(train.Store7, frequency = 52, start = c(2010,5), end = c(2012,42))
store7.fit <- tslm(trainStore7.ts[,3] ~ trend + season)
trainTSLMfor7 <- forecast(store7.fit, h = 53)
trainTSLMfor7
df7 <- rep(7, len = 53)
predict7 <- as.numeric(trainTSLMfor7$mean)
nrow7 <- data.frame(Store=df7,Date=dates,Weekly_Sales=predict7)
```


```{r}
train.Store8 <- train_final %>% filter(Store == 8)
trainStore8.ts <- ts(train.Store8, frequency = 52, start = c(2010,5), end = c(2012,42))
store8.fit <- tslm(trainStore8.ts[,3] ~ trend + season)
trainTSLMfor8 <- forecast(store8.fit, h = 53)
trainTSLMfor8
df8 <- rep(8, len = 53)
predict8 <- as.numeric(trainTSLMfor8$mean)
nrow8 <- data.frame(Store=df8,Date=dates,Weekly_Sales=predict8)
```


```{r}
train.Store9 <- train_final %>% filter(Store == 9)
trainStore9.ts <- ts(train.Store9, frequency = 52, start = c(2010,5), end = c(2012,42))
store9.fit <- tslm(trainStore9.ts[,3] ~ trend + season)
trainTSLMfor9 <- forecast(store9.fit, h = 53)
trainTSLMfor9
df9 <- rep(9, len = 53)
predict9 <- as.numeric(trainTSLMfor9$mean)
nrow9 <- data.frame(Store=df9,Date=dates,Weekly_Sales=predict9)
```


```{r}
train.Store10 <- train_final %>% filter(Store == 10)
trainStore10.ts <- ts(train.Store10, frequency = 52, start = c(2010,5), end = c(2012,42))
store10.fit <- tslm(trainStore10.ts[,3] ~ trend + season)
trainTSLMfor10 <- forecast(store10.fit, h = 53)
trainTSLMfor10
df10 <- rep(10, len = 53)
predict10 <- as.numeric(trainTSLMfor10$mean)
nrow10 <- data.frame(Store=df10,Date=dates,Weekly_Sales=predict10)
```


```{r}
train.Store11 <- train_final %>% filter(Store == 11)
trainStore11.ts <- ts(train.Store11, frequency = 52, start = c(2010,5), end = c(2012,42))
store11.fit <- tslm(trainStore11.ts[,3] ~ trend + season)
trainTSLMfor11 <- forecast(store11.fit, h = 53)
trainTSLMfor11
df11 <- rep(11, len = 53)
predict11 <- as.numeric(trainTSLMfor11$mean)
nrow11 <- data.frame(Store=df11,Date=dates,Weekly_Sales=predict11)
```


```{r}
train.Store12 <- train_final %>% filter(Store == 12)
trainStore12.ts <- ts(train.Store12, frequency = 52, start = c(2010,5), end = c(2012,42))
store12.fit <- tslm(trainStore12.ts[,3] ~ trend + season)
trainTSLMfor12 <- forecast(store12.fit, h = 53)
trainTSLMfor12
df12 <- rep(12, len = 53)
predict12 <- as.numeric(trainTSLMfor12$mean)
nrow12 <- data.frame(Store=df12,Date=dates,Weekly_Sales=predict12)
```


```{r}
train.Store13 <- train_final %>% filter(Store == 13)
trainStore13.ts <- ts(train.Store13, frequency = 52, start = c(2010,5), end = c(2012,42))
store13.fit <- tslm(trainStore13.ts[,3] ~ trend + season)
trainTSLMfor13 <- forecast(store13.fit, h = 53)
trainTSLMfor13
df13 <- rep(13, len = 53)
predict13 <- as.numeric(trainTSLMfor13$mean)
nrow13 <- data.frame(Store=df13,Date=dates,Weekly_Sales=predict13)
```


```{r}
train.Store14 <- train_final %>% filter(Store == 14)
trainStore14.ts <- ts(train.Store14, frequency = 52, start = c(2010,5), end = c(2012,42))
store14.fit <- tslm(trainStore14.ts[,3] ~ trend + season)
trainTSLMfor14 <- forecast(store14.fit, h = 53)
trainTSLMfor14
df14 <- rep(14, len = 53)
predict14 <- as.numeric(trainTSLMfor14$mean)
nrow14 <- data.frame(Store=df14,Date=dates,Weekly_Sales=predict14)
```


```{r}
train.Store15 <- train_final %>% filter(Store == 15)
trainStore15.ts <- ts(train.Store15, frequency = 52, start = c(2010,5), end = c(2012,42))
store15.fit <- tslm(trainStore15.ts[,3] ~ trend + season)
trainTSLMfor15 <- forecast(store15.fit, h = 53)
trainTSLMfor15
df15 <- rep(15, len = 53)
predict15 <- as.numeric(trainTSLMfor15$mean)
nrow15 <- data.frame(Store=df15,Date=dates,Weekly_Sales=predict15)
```


```{r}
train.Store16 <- train_final %>% filter(Store == 16)
trainStore16.ts <- ts(train.Store16, frequency = 52, start = c(2010,5), end = c(2012,42))
store16.fit <- tslm(trainStore16.ts[,3] ~ trend + season)
trainTSLMfor16 <- forecast(store16.fit, h = 53)
trainTSLMfor16
df16 <- rep(16, len = 53)
predict16 <- as.numeric(trainTSLMfor16$mean)
nrow16 <- data.frame(Store=df16,Date=dates,Weekly_Sales=predict16)
```


```{r}
train.Store17 <- train_final %>% filter(Store == 17)
trainStore17.ts <- ts(train.Store17, frequency = 52, start = c(2010,5), end = c(2012,42))
store17.fit <- tslm(trainStore17.ts[,3] ~ trend + season)
trainTSLMfor17 <- forecast(store17.fit, h = 53)
trainTSLMfor17
df17 <- rep(17, len = 53)
predict17 <- as.numeric(trainTSLMfor17$mean)
nrow17 <- data.frame(Store=df17,Date=dates,Weekly_Sales=predict17)
```


```{r}
train.Store18 <- train_final %>% filter(Store == 18)
trainStore18.ts <- ts(train.Store18, frequency = 52, start = c(2010,5), end = c(2012,42))
store18.fit <- tslm(trainStore18.ts[,3] ~ trend + season)
trainTSLMfor18 <- forecast(store18.fit, h = 53)
trainTSLMfor18
df18 <- rep(18, len = 53)
predict18 <- as.numeric(trainTSLMfor18$mean)
nrow18 <- data.frame(Store=df18,Date=dates,Weekly_Sales=predict18)
```


```{r}
train.Store19 <- train_final %>% filter(Store == 19)
trainStore19.ts <- ts(train.Store19, frequency = 52, start = c(2010,5), end = c(2012,42))
store19.fit <- tslm(trainStore19.ts[,3] ~ trend + season)
trainTSLMfor19 <- forecast(store19.fit, h = 53)
trainTSLMfor19
df19 <- rep(19, len = 53)
predict19 <- as.numeric(trainTSLMfor19$mean)
nrow19 <- data.frame(Store=df19,Date=dates,Weekly_Sales=predict19)
```


```{r}
train.Store20 <- train_final %>% filter(Store == 20)
trainStore20.ts <- ts(train.Store20, frequency = 52, start = c(2010,5), end = c(2012,42))
store20.fit <- tslm(trainStore20.ts[,3] ~ trend + season)
trainTSLMfor20 <- forecast(store20.fit, h = 53)
trainTSLMfor20
df20 <- rep(20, len = 53)
predict20 <- as.numeric(trainTSLMfor20$mean)
nrow20 <- data.frame(Store=df20,Date=dates,Weekly_Sales=predict20)
```


```{r}
train.Store21 <- train_final %>% filter(Store == 21)
trainStore21.ts <- ts(train.Store21, frequency = 52, start = c(2010,5), end = c(2012,42))
store21.fit <- tslm(trainStore21.ts[,3] ~ trend + season)
trainTSLMfor21 <- forecast(store21.fit, h = 53)
trainTSLMfor21
df21 <- rep(21, len = 53)
predict21 <- as.numeric(trainTSLMfor21$mean)
nrow21 <- data.frame(Store=df21,Date=dates,Weekly_Sales=predict21)
```


```{r}
train.Store22 <- train_final %>% filter(Store == 22)
trainStore22.ts <- ts(train.Store22, frequency = 52, start = c(2010,5), end = c(2012,42))
store22.fit <- tslm(trainStore22.ts[,3] ~ trend + season)
trainTSLMfor22 <- forecast(store22.fit, h = 53)
trainTSLMfor22
df22 <- rep(22, len = 53)
predict22 <- as.numeric(trainTSLMfor22$mean)
nrow22 <- data.frame(Store=df22,Date=dates,Weekly_Sales=predict22)
```


```{r}
train.Store23 <- train_final %>% filter(Store == 23)
trainStore23.ts <- ts(train.Store20, frequency = 52, start = c(2010,5), end = c(2012,42))
store23.fit <- tslm(trainStore23.ts[,3] ~ trend + season)
trainTSLMfor23 <- forecast(store23.fit, h = 53)
trainTSLMfor23
df23 <- rep(23, len = 53)
predict23 <- as.numeric(trainTSLMfor23$mean)
nrow23 <- data.frame(Store=df23,Date=dates,Weekly_Sales=predict23)
```


```{r}
train.Store24 <- train_final %>% filter(Store == 24)
trainStore24.ts <- ts(train.Store24, frequency = 52, start = c(2010,5), end = c(2012,42))
store24.fit <- tslm(trainStore24.ts[,3] ~ trend + season)
trainTSLMfor24 <- forecast(store24.fit, h = 53)
trainTSLMfor24
df24 <- rep(24, len = 53)
predict24 <- as.numeric(trainTSLMfor24$mean)
nrow24 <- data.frame(Store=df24,Date=dates,Weekly_Sales=predict24)
```


```{r}
train.Store25 <- train_final %>% filter(Store == 25)
trainStore25.ts <- ts(train.Store25, frequency = 52, start = c(2010,5), end = c(2012,42))
store25.fit <- tslm(trainStore25.ts[,3] ~ trend + season)
trainTSLMfor25 <- forecast(store25.fit, h = 53)
trainTSLMfor25
df25 <- rep(25, len = 53)
predict25 <- as.numeric(trainTSLMfor25$mean)
nrow25 <- data.frame(Store=df25,Date=dates,Weekly_Sales=predict25)
```


```{r}
train.Store26 <- train_final %>% filter(Store == 26)
trainStore26.ts <- ts(train.Store26, frequency = 52, start = c(2010,5), end = c(2012,42))
store26.fit <- tslm(trainStore26.ts[,3] ~ trend + season)
trainTSLMfor26 <- forecast(store26.fit, h = 53)
trainTSLMfor26
df26 <- rep(26, len = 53)
predict26 <- as.numeric(trainTSLMfor26$mean)
nrow26 <- data.frame(Store=df26,Date=dates,Weekly_Sales=predict26)
```


```{r}
train.Store27 <- train_final %>% filter(Store == 27)
trainStore27.ts <- ts(train.Store27, frequency = 52, start = c(2010,5), end = c(2012,42))
store27.fit <- tslm(trainStore27.ts[,3] ~ trend + season)
trainTSLMfor27 <- forecast(store27.fit, h = 53)
trainTSLMfor27
df27 <- rep(27, len = 53)
predict27 <- as.numeric(trainTSLMfor27$mean)
nrow27 <- data.frame(Store=df27,Date=dates,Weekly_Sales=predict27)
```


```{r}
train.Store28 <- train_final %>% filter(Store == 28)
trainStore28.ts <- ts(train.Store28, frequency = 52, start = c(2010,5), end = c(2012,42))
store28.fit <- tslm(trainStore28.ts[,3] ~ trend + season)
trainTSLMfor28 <- forecast(store28.fit, h = 53)
trainTSLMfor28
df28 <- rep(28, len = 53)
predict28 <- as.numeric(trainTSLMfor28$mean)
nrow28 <- data.frame(Store=df28,Date=dates,Weekly_Sales=predict28)
```


```{r}
train.Store29 <- train_final %>% filter(Store == 29)
trainStore29.ts <- ts(train.Store29, frequency = 52, start = c(2010,5), end = c(2012,42))
store29.fit <- tslm(trainStore29.ts[,3] ~ trend + season)
trainTSLMfor29 <- forecast(store29.fit, h = 53)
trainTSLMfor29
df29 <- rep(29, len = 53)
predict29 <- as.numeric(trainTSLMfor29$mean)
nrow29 <- data.frame(Store=df29,Date=dates,Weekly_Sales=predict29)
```


```{r}
train.Store30 <- train_final %>% filter(Store == 30)
trainStore30.ts <- ts(train.Store30, frequency = 52, start = c(2010,5), end = c(2012,42))
store30.fit <- tslm(trainStore30.ts[,3] ~ trend + season)
trainTSLMfor30 <- forecast(store30.fit, h = 53)
trainTSLMfor30
df30 <- rep(30, len = 53)
predict30 <- as.numeric(trainTSLMfor30$mean)
nrow30 <- data.frame(Store=df30,Date=dates,Weekly_Sales=predict30)
```


```{r}
train.Store31 <- train_final %>% filter(Store == 31)
trainStore31.ts <- ts(train.Store31, frequency = 52, start = c(2010,5), end = c(2012,42))
store31.fit <- tslm(trainStore31.ts[,3] ~ trend + season)
trainTSLMfor31 <- forecast(store31.fit, h = 53)
trainTSLMfor31
df31 <- rep(31, len = 53)
predict31 <- as.numeric(trainTSLMfor31$mean)
nrow31 <- data.frame(Store=df31,Date=dates,Weekly_Sales=predict31)
```


```{r}
train.Store32 <- train_final %>% filter(Store == 32)
trainStore32.ts <- ts(train.Store32, frequency = 52, start = c(2010,5), end = c(2012,42))
store32.fit <- tslm(trainStore32.ts[,3] ~ trend + season)
trainTSLMfor32 <- forecast(store32.fit, h = 53)
trainTSLMfor32
df32 <- rep(32, len = 53)
predict32 <- as.numeric(trainTSLMfor32$mean)
nrow32 <- data.frame(Store=df32,Date=dates,Weekly_Sales=predict32)
```


```{r}
train.Store33 <- train_final %>% filter(Store == 33)
trainStore33.ts <- ts(train.Store33, frequency = 52, start = c(2010,5), end = c(2012,42))
store33.fit <- tslm(trainStore33.ts[,3] ~ trend + season)
trainTSLMfor33 <- forecast(store33.fit, h = 53)
trainTSLMfor33
df33 <- rep(33, len = 53)
predict33 <- as.numeric(trainTSLMfor33$mean)
nrow33 <- data.frame(Store=df33,Date=dates,Weekly_Sales=predict33)
```


```{r}
train.Store34 <- train_final %>% filter(Store == 34)
trainStore34.ts <- ts(train.Store34, frequency = 52, start = c(2010,5), end = c(2012,42))
store34.fit <- tslm(trainStore34.ts[,3] ~ trend + season)
trainTSLMfor34 <- forecast(store34.fit, h = 53)
trainTSLMfor34
df34 <- rep(34, len = 53)
predict34 <- as.numeric(trainTSLMfor34$mean)
nrow34 <- data.frame(Store=df34,Date=dates,Weekly_Sales=predict34)
```


```{r}
train.Store35 <- train_final %>% filter(Store == 35)
trainStore35.ts <- ts(train.Store35, frequency = 52, start = c(2010,5), end = c(2012,42))
store35.fit <- tslm(trainStore35.ts[,3] ~ trend + season)
trainTSLMfor35 <- forecast(store35.fit, h = 53)
trainTSLMfor35
df35 <- rep(35, len = 53)
predict35 <- as.numeric(trainTSLMfor35$mean)
nrow35 <- data.frame(Store=df35,Date=dates,Weekly_Sales=predict35)
```


```{r}
train.Store36 <- train_final %>% filter(Store == 36)
trainStore36.ts <- ts(train.Store36, frequency = 52, start = c(2010,5), end = c(2012,42))
store36.fit <- tslm(trainStore36.ts[,3] ~ trend + season)
trainTSLMfor36 <- forecast(store36.fit, h = 53)
trainTSLMfor36
df36 <- rep(36, len = 53)
predict36 <- as.numeric(trainTSLMfor36$mean)
nrow36 <- data.frame(Store=df36,Date=dates,Weekly_Sales=predict36)
```


```{r}
train.Store37 <- train_final %>% filter(Store == 37)
trainStore37.ts <- ts(train.Store37, frequency = 52, start = c(2010,5), end = c(2012,42))
store37.fit <- tslm(trainStore37.ts[,3] ~ trend + season)
trainTSLMfor37 <- forecast(store37.fit, h = 53)
trainTSLMfor37
df37 <- rep(37, len = 53)
predict37 <- as.numeric(trainTSLMfor37$mean)
nrow37 <- data.frame(Store=df37,Date=dates,Weekly_Sales=predict37)
```


```{r}
train.Store38 <- train_final %>% filter(Store == 38)
trainStore38.ts <- ts(train.Store38, frequency = 52, start = c(2010,5), end = c(2012,42))
store38.fit <- tslm(trainStore38.ts[,3] ~ trend + season)
trainTSLMfor38 <- forecast(store38.fit, h = 53)
trainTSLMfor38
df38 <- rep(38, len = 53)
predict38 <- as.numeric(trainTSLMfor38$mean)
nrow38 <- data.frame(Store=df38,Date=dates,Weekly_Sales=predict38)
```


```{r}
train.Store39 <- train_final %>% filter(Store == 39)
trainStore39.ts <- ts(train.Store39, frequency = 52, start = c(2010,5), end = c(2012,42))
store39.fit <- tslm(trainStore39.ts[,3] ~ trend + season)
trainTSLMfor39 <- forecast(store39.fit, h = 53)
trainTSLMfor39
df39 <- rep(39, len = 53)
predict39 <- as.numeric(trainTSLMfor39$mean)
nrow39 <- data.frame(Store=df39,Date=dates,Weekly_Sales=predict39)
```


```{r}
train.Store40 <- train_final %>% filter(Store == 40)
trainStore40.ts <- ts(train.Store40, frequency = 52, start = c(2010,5), end = c(2012,42))
store40.fit <- tslm(trainStore40.ts[,3] ~ trend + season)
trainTSLMfor40 <- forecast(store40.fit, h = 53)
trainTSLMfor40
df40 <- rep(40, len = 53)
predict40 <- as.numeric(trainTSLMfor40$mean)
nrow40 <- data.frame(Store=df40,Date=dates,Weekly_Sales=predict40)
```


```{r}
train.Store41 <- train_final %>% filter(Store == 41)
trainStore41.ts <- ts(train.Store41, frequency = 52, start = c(2010,5), end = c(2012,42))
store41.fit <- tslm(trainStore41.ts[,3] ~ trend + season)
trainTSLMfor41 <- forecast(store41.fit, h = 53)
trainTSLMfor41
df41 <- rep(41, len = 53)
predict41 <- as.numeric(trainTSLMfor41$mean)
nrow41 <- data.frame(Store=df41,Date=dates,Weekly_Sales=predict41)
```


```{r}
train.Store42 <- train_final %>% filter(Store == 42)
trainStore42.ts <- ts(train.Store42, frequency = 52, start = c(2010,5), end = c(2012,42))
store42.fit <- tslm(trainStore42.ts[,3] ~ trend + season)
trainTSLMfor42 <- forecast(store42.fit, h = 53)
trainTSLMfor42
df42 <- rep(42, len = 53)
predict42 <- as.numeric(trainTSLMfor42$mean)
nrow42 <- data.frame(Store=df42,Date=dates,Weekly_Sales=predict42)
```


```{r}
train.Store43 <- train_final %>% filter(Store == 43)
trainStore43.ts <- ts(train.Store43, frequency = 52, start = c(2010,5), end = c(2012,42))
store43.fit <- tslm(trainStore43.ts[,3] ~ trend + season)
trainTSLMfor43 <- forecast(store43.fit, h = 53)
trainTSLMfor43
df43 <- rep(43, len = 53)
predict43 <- as.numeric(trainTSLMfor43$mean)
nrow43 <- data.frame(Store=df43,Date=dates,Weekly_Sales=predict43)
```


```{r}
train.Store44 <- train_final %>% filter(Store == 44)
trainStore44.ts <- ts(train.Store44, frequency = 52, start = c(2010,5), end = c(2012,42))
store44.fit <- tslm(trainStore44.ts[,3] ~ trend + season)
trainTSLMfor44 <- forecast(store44.fit, h = 53)
trainTSLMfor44
df44 <- rep(44, len = 53)
predict44 <- as.numeric(trainTSLMfor44$mean)
nrow44 <- data.frame(Store=df44,Date=dates,Weekly_Sales=predict44)
```


```{r}
train.Store45 <- train_final %>% filter(Store == 45)
trainStore45.ts <- ts(train.Store45, frequency = 52, start = c(2010,5), end = c(2012,42))
store45.fit <- tslm(trainStore45.ts[,3] ~ trend + season)
trainTSLMfor45 <- forecast(store45.fit, h = 53)
df45 <- rep(45, len = 53)
predict45 <- as.numeric(trainTSLMfor45$mean)
nrow45 <- data.frame(Store=df45,Date=dates,Weekly_Sales=predict45)

```

### WRITING THE OUTPUT INTO A CSV FILE

```{r}
output_format <- rbind(nrow1,nrow2,nrow3,nrow4,nrow5,nrow6,
                nrow7,nrow8,nrow9,nrow10,nrow11,nrow12,nrow13,nrow14,nrow15,nrow16,nrow17,nrow18,
                       nrow19,nrow20,nrow21,nrow22,nrow23,nrow24,nrow25,nrow26,nrow27,nrow28,nrow29,nrow30,
                       nrow31,nrow32,nrow33,nrow34,nrow35,nrow36,nrow37,nrow38,nrow39,nrow40,nrow41,nrow42,nrow43,nrow44,nrow45)

write.csv(output_format, file = "output.csv")
predictedSales <- output_format
```


```{r}
plot(predictedSales)
p1 <- ggplot() + 
    geom_col(aes(y = Weekly_Sales, x = Store), data = predictedSales)
p1
```

### Summary of predicted Sales by Store Type

```{r}
mean(output_format$Weekly_Sales)
```

# __CONCLUSION__
Store number 4 is predicted to have the highest amount of sales (3,808,117) on 2012-12-28 and store number 36 is predicted to have the least amount of sales (1,69,337.6 ) on 2013-11-01 and the average weekly sales of all stores from 2012-11-02 to 2013-11-01 is predicted to be 1,089,006.